Inference of Heating Properties from ``Hot'' Non-flaring Plasmas in Active Region Cores II. Nanoflare Trains

### 2016-06-17 hot_non-flaring_plasma_2/hot_non-flaring_plasma_2.tex
figure updates, minor text updates

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$.

@@

	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim4.5\times10^{-3}$. \hl{In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.} Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by 

@@

	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (electron or ion ), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$). All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}. All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.

@@

		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_electron_T0.pdf}

@@

		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_electron_T0.pdf}

@@

		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_ion_T0.pdf}

@@

		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_ion_T0.pdf}

>>>>

	where $c_2=\bar{T}_e/T_{e,a}\approx0.9$, $c_3=T_{e,0}/T_{e,a}\approx0.6$, $\nu_{ei}$ is the electron-ion binary Coulomb collision frequency and $\psi_{TR}$ is a term included to maintain charge and current and neutrality. These equations are closed by the equations of state $p_e=k_BnT_e$ and $p_i=k_BnT_i$. In the cases where we treat the plasma as a single-fluid, we use the original EBTEL model as described in \citet{klimchuk_highly_2008,cargill_enthalpy-based_2012}.
	\par The loop is heated by a prescribed heating function, applied to either the electrons ($\bar{Q}_e$) or the ions ($\bar{Q}_i$). Both species cool through a combination of thermal conduction ($F_{ce,0},\,F_{ci,0}$) and an enthalpy flux to the lower atmosphere, with the electrons also undergoing radiative cooling ($\mathcal{R_C}$). In the case of conductive cooling, a flux limiter, $F=(1/2)fnk_BTV_e$, is imposed to mitigate runaway cooling in a low-density, high-temperature plasma. In all cases we use a saturation limit of $f=1$. See \citetalias{barnes_inference_2016} for a discussion of how $f$ is likely to effect the presence of hot emission in a nanoflare-heated plasma.

@@

	\par Recent observations have suggested that loops in AR cores are maintained at an equilibrium temperature of $T_{peak}\approx4$ MK \citep{warren_constraints_2011,warren_systematic_2012}. Using our modified two-fluid EBTEL model, we have estimated the corresponding time-averaged volumetric heating rate for a loop of half-length $L=40$ Mm to be  $H_{eq}\sim3.6\times10^{-3}$. \hl{In the single-fluid EBTEL model, this value is slightly lower because losses due to electron-ion collisions are ignored.} Thus, to maintain an emission measure peaked about $T_{peak}$, for triangular pulses, the individual event heating rates are constrained by 

@@

	\par We now show the results of our loop simulations for each point in our multi-dimensional parameter space: species heated (single-fluid, electron or ion), power-law index ($\alpha$), heating frequency ($t_N$), and waiting-time/event energy relationship ($\beta$). All results were processed using the IPython system for interactive scientific computing in Python \citep{perez_ipython:_2007} as well as the NumPy and Scipy numerical and scientific Python libraries \citep{van_der_walt_numpy_2011}. All results were visualized using the matplotlib graphics library \citep{hunter_matplotlib:_2007}.

@@

		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_electron_T2.pdf}

@@

		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_electron_T2.pdf}

@@

		\includegraphics[width=\columnwidth]{figures/ratio_hist_alpha_ion_T2.pdf}

@@

		\includegraphics[width=\columnwidth]{figures/ratio_hist_twait_ion_T2.pdf}
